SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-24 docs/questioning.tex
add two dimensions + move back
more on subsection II.B

\subsection{Exploitation Model}

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we described in
the previous section. We base the analysis of the existing defenses on
this model. Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks ({\sc todo}).

An attack starts with the malicious user sending an request either to
the server or to a web user. In the first case the attacker could
upload data containing a specially crafted script (for example, in a
blog comment) or create a request with additional {\sc sql} code.

@@

>>>>

\subsection{Exploitation Model}
\label{sec:model}

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks ({\sc todo}).

An attack starts with the malicious user sending an request either to
the server or to a web user.
In the first case 
consider a web application that accepts and redisplays data of
uncertain origin without appropriate validation and / or filtering.
An attacker could upload data containing a specially
crafted script (for example, in a blog comment)
to steal the cookies of the visiting users
or embed malicious {\sc sql} code to retrieve all
the password entries from a database.
In the second case, the attacker crafts a malicious script
into a {\sc url} and then tricks an end user to click on it
via social engineering (i.e. phishing). In this way
an unauthorized command is transmitted from a user to a
website where a user is considered as legitimate.

Then, the injected code reaches the vulnerable
application where it probably becomes a part of a value
represented by a program variable.
In the next step, the code becomes a part of a query which
finally reaches the database where it is executed.
Attacks like {\sc sql} injection and {\sc csrf}
end right there.

Before we proceed with the {\sc xss} attack path,
we should mention here that there are two basic
{\sc xss} attack categories, namely:
{\it non-persistent} and {\it persistent}.
Non-persistent {\sc xss} attacks take place when the data provided
by a user, is used immediately by server-side scripts to parse
and display a page of results for and to that user, without
properly sanitizing the request. In the case of a
persistent {\sc xss} attack, malicious code
is saved by the server, and then permanently
displayed on the web site's pages that are displayed
to other users.

% A {\sc persistent} {\sc xss} attack though would
% continue
% An {\sc xss} attack that belongs to the {\it non-persistent}
% {\sc xss} category could have followed a different path.
% This is because

@@

\subsection{Detection Locus}

\subsection{Detection Circumvention}
